Supplementary Materials

### 2023-06-23 manuscript/supplementary.tex
ms updates

where $K_1$ and $H_1$ are the random change in neutral allele frequency change
due to offspring number (including heritable and non-heritable components), and
Mendelian segregation.

Now, let us look the variance of $\var(\Delta x_1)$ over evolutionary
replicates. Since the Mendelian random process and the offspring random process
are independent,

\begin{align}
  \var(\Delta x_1) &= \var(K_1) + \var(H_1).
\end{align}

Looking at each term,

\begin{align}
  \var(K_1) &\approx \frac{1}{4N^2} \sum_{i=1}^N \var\left(x_{0,i} (k_{0,i} - 1) \right)
\end{align}

where we ignore the covariance terms due to the sum, since these are on order
$\nicefrac{1}{N^3}$. In the first generation from an arbitrary starting point,
the neutral alleles assort independently into diploids with respect to their
fitness, so

@@

Assuming that no correlation between parental gametes (e.g. no inbreeding),
$\var(x_{0,i})$ is the binomial variance in individual allele frequency, or
$p_0(1-p_0)/2$, and $\var(k) := \var(k_{0,i})$ is the offspring variance of an
individual given by the reproduction process. For example, if the reproduction
process is a neutral multinomial Wright--Fisher, $\var(k) \approx 2$.

@@

\subsection{Misspecification of the Polygenic Selection Model}

Thus far, we have developed the general model of equation \eqref{XXX} by
assuming that the only source of $V_h$ is from the deleterious
mutation-selection-draft-drift process. However, other polygenic evolutionary
processes can also create, alter, and eliminate fitness variation. By assuming
that the only fitness variation originates from deleterious
mutation-selection-drift-draft processes, we introduce some model
misspecification. There are two main types of misspecification under the
selection model. First, non-polygenic positive selection processes, such as
recurrent sweeps, may create small-scale distortions in local genealogies.
These have been found to only impact diversity on small spatial scales
\parencite{Murphy2022-sj} in humans, and explain little of the total variation
in megabase-scale patterns of diversity. Second, there is model
misspecification due to our model assuming that the only polygenic selection
process happening is the flux of new deleterious mutations in, and their
eventual loss or fixation. Other polygenic selection processes could be
occurring, e.g. traits could be responding to directional selection. The
Santiago and Caballero model our work extends is very general, and can account
for multiple types of polygenic selection. The key input parameters are the
equilibrium heritable fitness variation $V_h$, and the variation introduced by
mutation each generation $V_m$.

Let us assume for now that,

\begin{align}
  \label{eq:Ne_inf}
  N_{e,\infty} \approx N \exp\left(-\frac{V_h + \varepsilon}{(1-Z) (2-(2-M) Z)} \right).
\end{align}

>>>>

where $K_1$ and $H_1$ are the random change in neutral allele frequency change
due to offspring number (including heritable and non-heritable components), and
Mendelian segregation in generation 1.

Now, let us look the variance of $\var(\Delta x_1)$ over evolutionary
replicates. Since the Mendelian segregation and the offspring random process
are independent,

\begin{align}
  \var(\Delta x_1) &= \var(K_1) + \var(H_1).
\end{align}
%
Looking at each term,

\begin{align}
  \var(K_1) &\approx \frac{1}{4N^2} \sum_{i=1}^N \var\left(x_{0,i} (k_{0,i} - 1) \right)
\end{align}
%
where we ignore the covariance terms due to the sum, since these are on order
$\nicefrac{1}{N^3}$. In the first generation from an arbitrary starting point,
the neutral alleles assort independently into diploids with respect to their
fitness, so we can simply the variance as

@@

Assuming no correlation between parental gametes (e.g. no inbreeding),
$\var(x_{0,i})$ is the binomial variance in individual allele frequency, or
$p_0(1-p_0)/2$, and $\var(k) := \var(k_{0,i})$ is the offspring variance of an
individual given by the reproduction process. For example, if the reproduction
process is a neutral multinomial Wright--Fisher, $\var(k) \approx 2$. Then, the
variance in allele frequency change due to non-heritable offspring number
variation is,

@@

% \subsection{Misspecification of the Polygenic Selection Model}

% Thus far, we have developed the general model of equation \eqref{XXX} by
% assuming that the only source of $V_h$ is from the deleterious
% mutation-selection-draft-drift process. However, other polygenic evolutionary
% processes can also create, alter, and eliminate fitness variation. By assuming
% that the only fitness variation originates from deleterious
% mutation-selection-drift-draft processes, we introduce some model
% misspecification. There are two main types of misspecification under the
% selection model. First, non-polygenic positive selection processes, such as
% recurrent sweeps, may create small-scale distortions in local genealogies.
% These have been found to only impact diversity on small spatial scales
% \parencite{Murphy2022-sj} in humans, and explain little of the total variation
% in megabase-scale patterns of diversity. Second, there is model
% misspecification due to our model assuming that the only polygenic selection
% process happening is the flux of new deleterious mutations in, and their
% eventual loss or fixation. Other polygenic selection processes could be
% occurring, e.g. traits could be responding to directional selection. The
% Santiago and Caballero model our work extends is very general, and can account
% for multiple types of polygenic selection. The key input parameters are the
% equilibrium heritable fitness variation $V_h$, and the variation introduced by
% mutation each generation $V_m$.

% Let us assume for now that,

% \begin{align}
%   \label{eq:Ne_inf}
%   N_{e,\infty} \approx N \exp\left(-\frac{V_h + \varepsilon}{(1-Z) (2-(2-M) Z)} \right).
% \end{align}
